% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jialong Chen}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{jialong.jalen.chen@gmail.com}{+1 (781)666-1340}{http://alepho.github.io}
\address{116 Russell Street}{Massachusetts State}{02453}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Brandeis University}, MA, USA}{2015 -- Present}
\textit{Master student} in Computer Science, expected January 2017
\datedsubsection{\textbf{University of Science and Technology of China(USTC)}, Hefei, China}{2011 -- 2015}
\textit{B.S.} in Applied Mathematics
\newline
Related courses: C Program Design, Fundamentals of Java Software Development, Data Structures and Database, Foundations of Algorithms, Operating System, Computer Organization

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C Java Python Scheme R MatLab
  \item Web Development: HTML+CSS JavaScript Rails SQL
  \item Platform: Unix-like
\end{itemize}


\section{\faUsers\ Experience}

\datedsubsection{\textbf{Intership, ICBC, Manhattan, NY}}{July 2016 -- Aug. 2016}
\role{R, Bloomberg API}{Summer Internship}
Data collecting and data analysing
\begin{itemize}
  \item Automatized and standardized department's data collection process from Bloomberg with R scripts and Bloomberg API.
  \item Analyzed data with machine learning techniques, including classification and clustering algorithms.
\end{itemize}


\datedsubsection{\textbf{Pocket Guide}}{Oct. 2015 -- Dec. 2015}
\role{Android, C, Java, JNI, Socket}{Course Final Project, collaborate with Tianjie Zhong, Chao Liu}
An Android App with a Linux server, https://github.com/alepho/boom-shakalaka
\begin{itemize}
  \item With original intention to collaborate with people with Java background, introduced JNI to create daemon on the Linux server
  \item Implemented the concurrent part in the App, as well as the server program
  \item Optimized A+
\end{itemize}

\datedsubsection{\textbf{Neuron network for science problems}}{Oct. 2015 -- Dec. 2015}
\role{Python}{Course Final Project(Kaggle competition), collaborate with Hui Sun, Shuyi Lei}
AI for science questions, https://github.com/alepho/AITeamProject
\begin{itemize}
  \item Used science textbooks from open resources project as learning materials, to train a neuron network for multiple choice science questions.
  \item Contributed all the code with the ideas of the whole group.
  \item Optimized A
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://aleph0.me
  \item GitHub Page: http://alepho.github.io
  \item Active member of Linux User Group(LUG) in USTC
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
