% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\hypersetup{pdfauthor={Jialong Chen},%
            pdftitle={Resume of Jialong Chen},%
            pdfkeywords={resume, Jialong Chen, software engineer, new graduate, full stack, front end, back end, android, big data},%
            urlcolor = darkblue
}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jialong Chen}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{\href{mailto:jialong.jalen.chen@gmail.com}{jialong.jalen.chen@gmail.com}}{+1 (781)666-1340}{\href{https://alepho.github.io}{https://alepho.github.io}}
\address{9373 Hemlock Dr, Richmond}{BC, Canada}{V6Y 4K6}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}
 
\section{\texorpdfstring{\faGraduationCap}\ \ Education}
\datedsubsection{\textbf{Brandeis University}, MA, USA}{Aug. 2015 -- Jan. 2017}
\textit{Master} in Computer Science. \textit{Received the degree one term earlier than designed.}

\datedsubsection{\textbf{University of Science and Technology of China(USTC)}, Hefei, China}{Aug. 2011 -- June. 2015}
\textit{B.S.} in Applied Mathematics



\section{\texorpdfstring{\faCogs}\ \ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java(expert), C(proficient), Python, Scheme, R, MatLab(prior experience)
  \item Web Development: HTML+CSS, JavaScript, Node, SQL
  \item OSs: Windows, Unix-like, Android
  \item Platforms: Docker, Hadoop
\end{itemize}



\section{\texorpdfstring{\faUsers}\ \ Experience \& Coursework}

\datedsubsection{\textbf{Teaching Assistant, Brandeis University, MA}}{Aug. 2016 -- Dec. 2016}
\role{IntelliJ IDEA, Android}{for COSI 153a Mobile Application Development}
\begin{itemize}
  \item Supported the lecturer in creating successful learning environment. Worked together to adjust the course content and arrangement in accordance with changes in the system and IDE in Android API level 23.
  \item Plugin development for Android Studio with Java and IntelliJ IDEA API. 
  \newline
  Example: \href{https://github.com/alephO/AndroidExporter}{https://github.com/alephO/AndroidExporter}
  \item Helped students on individual and small groups to solve their problems and improve their academic performance. Graded students' homeworks.
\end{itemize}

\datedsubsection{\textbf{Internship, ABC NY Branch, Manhattan, NY}}{June 2016 -- Aug. 2016}
\role{R, Bloomberg API} \null
Data collection and data analysis
\begin{itemize}
  \item Automatized and standardized department's data collection process from Bloomberg terminal with R scripts and a CRAN package Rblpapi, reducing operating time by 75\%. Designed UI in R script with the gWidgetstcltk package for the convenience of people without CS background.
  \item Analyzed data and built models for increase rate and market relevance according to their GICS catalogs, with machine learning techniques, including classification and clustering algorithms, like k-mean and AGNES.
\end{itemize}

\datedsubsection{\textbf{Pocket Guide}}{Oct. 2015 -- Dec. 2015}
\role{Android, C, Java, JNI, Socket}{Course Final Project, collaborate with Tianjie Zhong, Chao Liu}
An Android App with a Linux server, \href{https://github.com/alepho/boom-shakalaka}{https://github.com/alepho/boom-shakalaka}
\begin{itemize}
  \item Implemented the server to communicate with Apps concurrently, with Java threads and TCP Sockets.  
  \item Introduced JNI to interact create daemon on the Linux server, making use of C's native communication with UNIX, with original intention to collaborate with people with Java background.
  \item Designed AsyncTasks in the Android App to implemented the concurrent part and the communication part. 
\end{itemize}




% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\texorpdfstring{\faInfo}\ \ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \href{https://aleph0.me}{https://aleph0.me}
  \item GitHub Page: \href{https://alepho.github.io}{https://alepho.github.io}
  \item Active member of Linux User Group(LUG) in USTC
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
